BERT Model Compression and Weight Sharing

### 2019-05-11 paper/paper.tex
Add bibliography
First paragraph on KD

\section{Background}
Deep Neurel Networks (DNNs) have become extremely large in size with growing complexities. A BERT base model has 110M parameters and takes 438 MB disk space to store. This makes it very hard to deploy those models on mobile devices, which in most cases have limited storage and RAM and lower computational resources. The challenge that we are facing is how to compress DNNs in size while keeping their predictive performance competitive with full model.

@@

@@

Example Structure:
\begin{itemize}
\item What 3-5 papers have been published in this space?
\item How do these  differ from your approach?
\item What data or methodologies do each of these works use?
\item How do you plan to compare to these methods?
\end{itemize}

@@

\section{Inference (or Training)}

@@

\bibliography{example}
\bibliographystyle{icml2017}

>>>>

\section{Background}

@@

Deep Neurel Networks (DNNs) have become extremely large in size with growing complexities. A BERT base model has 110M parameters and takes 438 MB disk space to store. This makes it very hard to deploy those models on mobile devices, which in most cases have limited storage and RAM and lower computational resources. The challenge that we are facing is how to compress DNNs in size while keeping their predictive performance competitive with full model.

@@

% Example Structure:
% \begin{itemize}
% \item What 3-5 papers have been published in this space?
% \item How do these  differ from your approach?
% \item What data or methodologies do each of these works use?
% \item How do you plan to compare to these methods?
% \end{itemize}

We are interested in compressing the language representation model BERT \cite{devlin2018bert}. It is the state-of-art result in many natural language processing tasks such as natural language inference, paraphrasing and named entity recognition.

\cite{cheng2017survey} provides a comprehensive overview of the state-of-art methods to compress DNNs. Of the methods summarized by the paper, the ones that are of interest to our work are weight-pruning and quantization \cite{han2015deep}, and low-rank factorization \cite{denton2014exploiting}. Knowledge distillation, first proposed by \cite{bucilua2006model} as ``knowledge transfer'', was recently popularized by \cite{hinton2015distilling}. It differs from the previously mentioned methods since it compresses an existing model by replacing it with a simpler model that is trained on its outputs.

DeepTwist, a end-to-end training framework, allows us to incorporate compression procedures into training \cite{lee2018deeptwist}. Under this framework, the model parameters are occasionally distorted during training time instead of only at the end. This framework has the benefit of simplified training procedure and faster convergence and reduced requirement for hyperparameter tuning. Experiment on MNIST dataset with DeepTwist shows that LeNet-5 and LeNet-300-100 models are able to retain predictive accuracy under high compression rate.

@@

\section{Inference (or Training)}
\label{sec:training}

\subsection{Knowledge Distillation}
\label{subsec:kd}

In this paper, we limit our purview to text classification tasks. Training
neural-network-based systems for this task typically consists of a form of
gradient descent based on a differentiable loss function which takes in the
prediction for a given example and the correct label. That is, if we have
training data $(\bm{x}_i, y_i)$ and model $f$, we would aim to minimize,
\[ \ell(f(\bm{x_i}), y_i)\]
where usually the loss function is taken to be Cross-Entropy loss. When we
already have a model $f$ that performs well, we can leverage this training
paradigm through a modification called \emph{knowledge distillation}. Given the
large model that performs well, termed the \emph{teacher network}, we train a
smaller network $g$, the \emph{student network}, by minimizing,
\[ \ell(g(\bm{x_i}), f(\bm{x_i})).\]
Here, we can no longer use Cross-Entropy loss because $f(\bm{x}_i)$ is a
probability distribution rather than a specific label. However, we can take
$\ell$ to be either mean-square error (MSE) between the probabilities in
log-space, or Kullback-Leibler (KL) loss. We avoid MSE error on the
probabilities themselves because of disappearing gradients when the predicted
probabilities are very close to 0 or 1.

% TODO: talk about KD

\subsection{Deep Twist}

% TODO: talk about DeepTwist™

@@

\bibliography{paper}
\bibliographystyle{icml2017}
